---
title: "fishblicc Support & Package Creation"
author: "Paul Medley"
date:   "August 2022"
format: html
editor: visual
---

# Package Guide

The general guide is from

[R Packages (2e) (r-pkgs.org)](https://r-pkgs.org/)

by Wickham and Bryan.

Specific to this package, rstantools were used. An excellent guide was provided by

```{r setup}
library("here")
library("devtools")
library("usethis")

#usethis::use_build_ignore("Package_Creation.qmd")

#create_package(here())


# system2("powershell", args=c("Set-Content", "-Path", paste0(here(),"\\.Rproj.user"), "-Stream", "com.dropbox.ignored", "-Value", "1"))
#system2("powershell", args=c("Set-Content", "-Path", paste0(here(),"\\.git"), "-Stream", "com.dropbox.ignored", "-Value", "1"))
#system2("powershell", args=c("Set-Content", "-Path", paste0(here(),"\\.gitignore"), "-Stream", "com.dropbox.ignored", "-Value", "1"))

#packageVersion("devtools")
use_git()  # Sets up git. Needed only once
usethis::use_github() # sets up on github
# https://github.com/settings/tokens
# gitcreds::gitcreds_set()

```

# To Do

# Other Package Dependencies

```{r }
#| label: SetUpPackages
#| eval: false
#use_testthat(3)   # Sets up testing skeleton

# add additional package dependencies
usethis::use_package("stats")
#usethis::use_package("statmod")
usethis::use_package("ggplot2")
usethis::use_package("tidyr")
usethis::use_package("dplyr")
usethis::use_package("purrr")
usethis::use_package("tibble")
usethis::use_package("tidyselect")
usethis::use_package("flextable")
usethis::use_tidy_description()   #orders and formats DESCRIPTION fields
```

# Package Build

```{r }
#| label: BuildPackage
#| eval: false
#remove.packages("JABBAHCR")

# Following compiles Stan code and creates the package
# Needs to be run twice apparently for initial set up
#example(source)
#try(roxygen2::roxygenize(load_code = sourceDir), silent=TRUE)
roxygen2::roxygenize()  

# Build package
# compile first - clean and install

# If Add new Stan file, e.g., inst/stan/new.stan
pkgbuild::compile_dll() # to preform a fake R CMD install.
#roxygen2::roxygenize()  # to update the documentation etc.

devtools::document()  # only updates documentation
```

# Test That

```{r }
#| label: test_that
#| eval: false

use_r("JBH_Create")
use_r("JBH_HCRTest")
use_r("JBH_SimOutput")
use_r("JBH_Misc")

#use_testthat(3)   # Sets up testing skeleton
use_test("JBH_Create")
use_test("JBH_HCRTest")
use_test("JBH_SimOutput")
use_test("JBH_Misc")

```

# Install Package

```{r }
#| label: CheckPackage
#| eval: false
check()    # Checks package is OK

# rstantools removed from imports

load_all()  # To test functions as though they are installed as package
#devtools::install()     # to install the package locally.

remove.packages("JABBAHCR")
# install the package locally

install.packages("../JABBAHCR", repos=NULL, type="source")

# install from github
remotes::install_github("PaulAHMedley/JABBAHCR")

```


# Create Data Sets

```{r DataCreation}

#load(here("data", "seatrout_ld.rda"))
#save(trgl_ld, trgl_slim, trgl_rp, file=here("output", "blicc_results.rda"))
#load("D:/paula/Dropbox/Routines/BLICC/output/blicc_results.rda")

usethis::use_data(data, compress="xz", overwrite=T)
```

# TEST RUNS

# Testing

For the effort control to work in the HCR simulation, it must be converted to fishing mortality. A linear relationship is assumed between effort and fishing mortality applied in the model, based on the median harvest rate estimated in each year. This is estimated using a simple linear model of the estimated fishing mortality dependent on the estimate of the standardised effort passing through the origin. The conversion factor (`rho`) was estimated to convert the stated control value in the HCR to fishing mortality. Note that effort used in the current rule is month based rather than yearly as required in the JABBA-based rule, so that is taken into account in estimating the conversion factor `rho`. For the annual models, the effort would apply for an entire year and for the quarterly model, the effort level would be re-evaluated every 3 months. In practice, the rule is applied quarterly to allow a more rapid response.

```{r}
load_all()

fmort_Y_df <- dplyr::select(jabba_fit$kbtrj, year, H) |>
  dplyr::filter(H > 0.0, H < 1.0) |>
  dplyr::mutate(f = -log(1-H)) |>
  dplyr::group_by(year) |>
  dplyr::summarise(f = median(f), , .groups="drop") 

effort_Y_df <- jabba_fit$inputseries$catch |>
  dplyr::inner_join(jabba_fit$inputseries$cpue, by="Year") |>
  dplyr::filter(! is.na(cpue)) |>
  dplyr::mutate(Effort = 1000*catch/(cpue*12)) 

fmort_Y_df <- fmort_Y_df |>
  dplyr::left_join(effort_Y_df, by=c("year" = "Year")) |>
  dplyr::filter(! is.na(Effort))
rho_Y <- lm(formula= f ~ Effort + 0, data=fmort_Y_df)$coef[1]

ref_pt <- MSY_refpt(jabba_fit, ref_year=2022)

HCR <- create_HCR_MSE(jabba_fit, 
                      control_type = "Effort",
                      rho = 1/rho_Y,
                      ProjLength=50, 
                      ref_pt = standard_risk_ref_pt(m = median(jabba_fit$pars_posterior$m)),
                      nsim=1000)

HCR_sim <-  with(ref_pt, HCR(c(IMSY, IMSY), c(fMSY, fMSY), change_limit=NA, ma=0.5))

suppressWarnings(print(graph_sim_BMSY_FMSY(HCR_sim)))

```





```{r }
#| label: TestSetup1
#| eval: false
load_all()
#load(file=here("data", "jabba_seabob.rda"))

ref_pt <- MSY_refpt(jabba_seabob, ref_year=2022) #used to set HCR

HCR <- create_HCR_MSE(jabba_seabob, 
                       control_type = "Effort",
                       ProjLength=50, 
                       nsim=1000)

HCR_sim <- with(ref_pt, HCR(c(IMSY, IMSY), c(fMSY, fMSY), change_limit=NA, ma=0.5))

graph_sim_BMSY_FMSY(HCR_sim)
table_sim_status(HCR_sim)
table_sim_decision(HCR_sim)
table_sim_performance(HCR_sim)
```



```{r}
#| label: TestSetup2
#| eval: true

IMSY = ref_pt$IMSY
fMSY = ref_pt$fMSY
rel_index_range = c(0.5, 1.2)
rel_control_range = c(0.0, 1.2)
NInflex = 2
NBreaks = 5 
change_limit = c(NA, 0.05, 0.15)
ma = c(0.25, 0.5, 0.75)


Control_Type <- "Effort"  # Effort or Catch
TestHCR_df <- define_HCR_test_range(ref_pt$IMSY, ref_pt$fMSY, 
                         rel_index_range = c(0.5, 1.2),
                         rel_control_range = c(0.0, 1.2), 
                         NInflex = 2, 
                         NBreaks = 5, 
                         change_limit = c(NA, 0.05, 0.15), 
                         ma = c(0.25, 0.5, 0.75)) |>
              dplyr::filter(purrr::map_lgl(trControl, ~ sum(.) > 0)) # remove no fishing HCR

graph_linear_HCR(TestHCR_df)

```


```{r }
#| label: Run_HCR2
#| eval: true
#| output: false
load_all()
nsim <- 1000
risk_rp <- standard_risk_ref_pt()

HCR_res <- run_HCR_MSE_list(
    jabba_seabob, 
    TestHCR_df, 
    control_type = "Effort",
    ProjLength=50, 
    nsim = nsim,
    ref_pt = risk_rp)

```
```{r}
graph_HCR_catches(HCR_res)
graph_HCR_status(HCR_res, HCR)
graph_HCR_decision(HCR_res)
graph_HCR_status_catches(HCR_res)
```


```{r}
CandidateHCR_df <- HCR_res |>
  dplyr::filter(Evaluation=="Candidate")
graph_HCR_status_catches(CandidateHCR_df)
CandidateHCR_df |>
  dplyr::arrange(desc(State)) |>
  head(n=5) |>
  graph_linear_HCR(HCR_ID=TRUE)
```
```{r}
BestHCR <- CandidateHCR_df |>
  dplyr::arrange(Rank) |>
  head(12)
graph_linear_HCR(BestHCR, HCR_ID=TRUE)
table_HCR_performance(BestHCR)
```


# Authentication

```{r}
# Get token from website and set in R
# https://github.com/settings/tokens
gitcreds::gitcreds_set()

```
